### 2013-12-03 Publications/2013-ISBI14/03-methods.tex
Fixing reviews

Finally, for evaluating \Gls*{t2b},
we fine-tuned \emph{ANTs} \cite{avants_ants:_2013},
in order to register \textit{b0} to T2. To this end, we used a
multi-resolution scheme with 3 levels of subsampling and smoothing,
mutual information metric, and symmetric diffeomorphic transform 
(\texttt{SyN}). Several configurations of kernel widths for the 
regularization smoothers were tested, and finally selected 
0.5/1.0 voxels (gradient/deformation fields, respectively) 
for its best result. Additionally, undistorted images are 
corrected for dropout using the determinant
of the Jacobian of the deformation field.

@@

The evaluation framework is completed by automated 
assessment modules. We evaluated three characteristics
of the correction methods. 
Firstly, we assessed the geometrical correctness
reporting overlap indices of three tissue
probability maps (namely \gls*{csf}, \gls*{wm},
and \gls*{gm}), weighting the average by tissue
volumes.
Secondly, to evaluate the quality of the actual 
signal dropout correction, we studied the 
similarity volume by volume computing the $\ell_1$-norm
correlation index. We report this score
on the \textit{b0} and the average of the remaining \gls*{dwi}
volumes. Thirdly, we studied the impact on the
connectivity matrices reporting the number of
false positives (inexistent connections in the
gold-standard) and false negatives (or missed connections).

>>>>

Finally, for evaluating \Gls*{t2b},
we fine-tuned \emph{ANTs} (\url{http://stnava.github.io/ANTs}),
in order to register \textit{b0} to T2. To this end, we used a
multi-resolution scheme with 3 levels of subsampling and smoothing,
mutual information metric, and symmetric diffeomorphic transform 
(\texttt{SyN}). Several configurations of kernel widths for the 
regularization smoothers were tested, and finally selected 
0.5/1.0 voxels (gradient/deformation fields, respectively) 
for its best result. Additionally, undistorted images are 
corrected for dropout using the determinant
of the Jacobian of the deformation field.

@@

The evaluation framework is completed by automated 
assessment modules. We evaluated three characteristics
of the correction methods. 
Firstly, we assessed the geometrical correctness
reporting overlap indices of three tissue
probability maps (namely \gls*{csf}, \gls*{wm},
and \gls*{gm}), weighting the average by tissue
volumes.
Secondly, to evaluate the quality of the actual 
signal dropout correction, we studied the 
similarity volume by volume computing the $\ell_1$-norm
correlation index. We report this score
on the \textit{b0} and the average of the remaining \gls*{dwi}
volumes. Thirdly, we studied the impact on the
connectivity matrices reporting the number of
false positives (nonexistent connections in the
gold-standard) and false negatives (or missed connections).

### 2013-12-03 Publications/2013-ISBI14/04-results.tex
Fixing reviews

\begin{figure*}[tpb]
   \centering
   \includegraphics[width=0.9\textwidth]{Fig02-Results}
   \caption{Visual evaluation of the correction methods.
   First row represents a coronal section of the \textit{b0} volume. 
   In second row, the outcome of tractography after filtering tracks
   that did not connect two regions.
   Third row shows the associated connectivity matrices. All the matrices
   are compared to the ground-truth connections in the phantom. The existing
   connections that were correctly detected at each step are depicted in white
   color. False positives have been marked in red and false negatives in blue.
   Gray color represents the true negatives (non-existent connections correctly detected).}
   \label{fig:results}
\end{figure*}

@@

Although we found connectivity matrices rather invariant with
respect distortion, they are suspected to be significantly
impacted by the susceptibility artifact on real data 
\cite{irfanoglu_effects_2012}.
This hypothesis points to the need of more appropriate 
phantoms with denser connectivity matrices.
State of the art phantoms for tractography usually present a
discrete set of simulated fiber bundles that translate in 
very sparse fiber-endings regions and connectivity matrix.
In the real case, the surface limiting the tracks is densely 
covered by the regions mapped from the anatomical 
dataset, what leads to larger sensitivity with respect 
deformations.

>>>>

\begin{figure*}[tpb]
   \centering
   \includegraphics[width=0.80\textwidth]{Fig02-Results}
   \caption{Visual evaluation of the correction methods.
   First row represents a coronal section of the \textit{b0} volume. 
   In second row, the outcome of tractography after filtering tracks
   that did not connect two regions.
   Third row shows the associated connectivity matrices. All the matrices
   are compared to the ground-truth connections in the phantom. The existing
   connections that were correctly detected at each step are depicted in white
   color. False positives have been marked in red and false negatives in blue.
   Gray color represents the true negatives (non-existent connections correctly detected).}
   \label{fig:results}
\end{figure*}

@@

Although we found connectivity matrices rather invariant with
respect to distortion, they are suspected to be significantly
impacted by the susceptibility artifact on real data 
\cite{irfanoglu_effects_2012}.
This hypothesis points to the need of more appropriate 
phantoms with denser connectivity matrices.
State of the art phantoms for tractography usually present a
discrete set of simulated fiber bundles that translate in 
very sparse fiber-endings regions and connectivity matrix.
In the real case, the surface limiting the tracks is densely 
covered by the regions mapped from the anatomical 
dataset, what leads to larger sensitivity with respect to
deformations.
